Can greedy-like heuristics be useful for solving the Weighted Orthogonal Art Gallery Problem under regular grid discretization?

### 2020-10-11 doc/paper.tex
komentari na Milanov tekst

	Treba primjetiti da iz pokrivenosti diskretizacije D(P) skupom stražara iz Z ne slijedi pokrivenost poligona P istim skupom stražara Z. Na slici 1.1 pod a) prikazan je poligon koji nije pokrivan, dok je njegova diskretizacija pokrivena. Trokut na dnu poligona predstavlja nepokrivenu regiju. Poligon na slici 1.1 pod b) je pokriven kao i njegova diskretizacija.

@@

	Couto et al.~\cite{couto2007exact} koristili su pomenutu diskretizaciju za problem ortogonalne galerije. U njihovom radu broj pologona nad kojim je primjenjena ova diskretizacija je 10282. Za 59.4\% poligona je vazilo da iz pokrivenoosti diskretnog skupa D(P) slidi pokrivensort poligona P za optimalno pronadjen skup strazara koji pokrivaju D(P). Oni su dodavali nove tačke u D(P) iz nepokrivenih regija kako bi iz pokrivenosti diskretizacije slijedila pokrivenost poligona za sve poligone. Nad testiranim uzorkom se pokazalo da se broj novododanih tačaka može opisati regresivnom funkcijom  0.003·n+1.1, gjde je n broj tjemena poligona. Dakle, ili je čitav poligon pokriven ili mali broj regija je nepokriveno optimalnim skupom stražara Z za D(P). U sekciji 4 će biti prikazana površina ovih nepokrivenih regija.

@@

     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~(\ref{large_w0}): the exact \textsc{Cplex} approach is a clear winner concerning average solutions' quality as well as the average runtimes;  the best heuristic algorithm w.r.t. solution quality is \textsc{Greedy-2 +Cplex}. It also matches in the most cases (on 6 instances) to the optimum results w.r.t. other heuristic approaches. Its average results are within 22\% of the average of  optimal solutions.  The pure \textsc{Greedy-1} slightly outperforms the pure greedy \textsc{Greedy-2}. It is interesting that \textsc{Greedy-1} assigns in average a  higher number of guards in comparison to the average number of guards of \textsc{Greedy-2}. The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach. Reason for that can be seen in the used regular discretization of the polygon. For the polygons with a larger area, more points are involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller (which was the case of \emph{Minarea} polygons).
     	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithms w.r.t. solution quality is \textsc{Greedy-1+Cplex} which is able to match in 96 instances the quality of optimal solutions. Slightly worse results are delivered by \textsc{Greedy-1} and \textsc{Greedy-2}. The obtained (heuristic) solutions of these two approaches are within 1\% of optimal solutions and they are
     	able to reach the quality of the optimal solution for 92 instances. Unfortunately, the runtimes in comparison to the runtimes of \textsc{Cplex} are significantly higher for all of our heuristic approaches. However, the average runtime for \textsc{Cp} is a bit higher that the avg. runtimes of the heuristic approaches. Again, average standard deviation for each heuristic method is rather small, indicating the good quality of the proposed algorithms.
     	\item \fxnote{TODO: pokrivenost...}
     \end{itemize}
    \fxnote{Milan: generisati vrijeme izvrsavanja...--- Kog izvrsavanja?}

    \begin{figure}
    	\centering
    	\includegraphics[width=\textwidth]{grafikon1.eps}
    	\caption{Polygon Coverage}
    	\label{fig:cov}
    \end{figure}

>>>>

	Treba primjetiti da iz pokrivenosti diskretizacije D(P) skupom stražara iz Z ne slijedi pokrivenost poligona P istim skupom stražara Z. Na slici 1.1\fxnote{pogresna referenca 1.1, mislis na 1...} pod a) prikazan je poligon koji nije pokrivan, dok je njegova diskretizacija pokrivena. Trokut na dnu poligona predstavlja nepokrivenu regiju. Poligon na slici 1 pod b) je pokriven kao i njegova diskretizacija. \fxnote{Milane, mislm da ti slika pod a) ne odgovara svrsi. Recimo ovaj poligon se cak moze pokriti sa jednim covrom, jesam u pravu? Treba nam poligon koji se ne moze pokriti bilo kojim odabirom cvorova (cuvara)?}

@@

	Couto et al.~\cite{couto2007exact} koristili su pomenutu diskretizaciju za problem ortogonalne galerije. U njihovom radu broj pologona nad kojim je primjenjena ova diskretizacija je 10282. Za 59.4\% poligona je vazilo da iz pokrivenoosti diskretnog skupa D(P) slidi pokrivenost poligona P za optimalno pronadjen skup strazara koji pokrivaju D(P)\fxnote{Sta je sa ostalim poligonima koji nisu bili pokriveni? Koliki je procenat pokrivenosti bio u tom slucaju? Kako se ovo odnosi na druge diskretizacije, bilo je puno bolje ili?}. Oni su dodavali nove tačke u D(P) iz nepokrivenih regija kako bi iz pokrivenosti diskretizacije slijedila pokrivenost poligona za sve poligone. Nad testiranim uzorkom se pokazalo da se broj novododanih tačaka može opisati regresivnom funkcijom  0.003·n+1.1, gdje je n broj tjemena poligona. Dakle, ili je čitav poligon pokriven ili mali broj regija je nepokriveno optimalnim skupom stražara Z za D(P). U sekciji 4 će biti prikazana površina ovih nepokrivenih regija.

@@

     	\item In case of the instances that include large-area polygons ($FAT$) and weight $W0$ (Table~(\ref{large_w0}): the exact \textsc{Cplex} approach is a clear winner concerning average solutions' quality as well as the average runtimes;  the best heuristic algorithm w.r.t. solution quality is \textsc{Greedy-2 +Cplex}. It also matches in the most cases (on 6 instances) to the optimum results w.r.t. other heuristic approaches. Its average results are within 22\% of the average of  optimal solutions.  The pure \textsc{Greedy-1} slightly outperforms the pure greedy \textsc{Greedy-2}. It is interesting that \textsc{Greedy-1} assigns in average a  higher number of guards in comparison to the average number of guards of \textsc{Greedy-2}. The runtimes of our heuristic approaches are an order of magnitude lower than the time of \textsc{Cplex} approach. Reason for that can be seen in the used regular discretization of the polygon. For the polygons with a larger area, more points are involved in the discrete set $D(P)$ and, therefore, iterations of greedy methods take a longer time than in case when $D(P)$ is smaller (which was the case of \emph{Minarea} polygons).
     	\item  In case of the instances that include large-area polygons ($FAT$) and weight $W1$ (Table~(\ref{large_w1}): the best heuristic algorithms w.r.t. solution quality is \textsc{Greedy-1+Cplex} which is able to match in 96 instances the quality of optimal solutions. Slightly worse results are delivered by \textsc{Greedy-1} and \textsc{Greedy-2}. The obtained (heuristic) solutions of these two approaches are within 1\% of optimal solutions and they are
     	able to reach the quality of the optimal solution for 92 instances. Unfortunately, the runtimes in comparison to the runtimes of \textsc{Cplex} are significantly higher for all of our heuristic approaches. However, the average runtime for \textsc{Cp} is a bit higher that the avg. runtimes of the heuristic approaches. Again, average standard deviation for each heuristic method is rather small, indicating the good quality of the proposed algorithms.
     	\item \fxnote{TODO: pokrivenost...}
     \end{itemize}
    \fxnote{Milan: generisati vrijeme izvrsavanja svakog od algoritama, dakle, $x$-osa predstavlja sljedece parove: (Smallarea, W0), (Smllarea, W1), (FAT, W0), (FAT, W1), i onda za svaku od ovih kategorija, prikazi box-plotove za 6 nasih algoritama koji prikazuju njihova vremena izvrsavnja na $y$ osi (predstavi ih razlicitim bojama, ubaci i liegendu u gornjem desnom uglu) -- ove brojeve nadji u Tabelama 1-4,  kolona 3 ($t[s]$). U zavisnosti od prikaza, koristiti log skaliranje za y-osu.... }

    \begin{figure}
    	\centering
    	\includegraphics[width=\textwidth]{grafikon1.eps}
    	\caption{Polygon Coverage \fxnote{Kako si podlijelio instance sa tezinama W0 i W1? Ovo je za Cplex? Ja bih prikazao ovo ipak sa dva dijagrama, jedan za W0, a drugi za W1)}}
    	\label{fig:cov}
    \end{figure}
